Matching bullets

### 2015-11-20 imaging-paper.Rnw
Discuss lighting options

>>>>

Several lighting options are available to tweak in order to highlight markings in on the bullets more strongly:

\begin{enumerate}
    \item \textbf{Ambient Lighting} - Lighting which is used to simulate the light naturally present in the environment.
    \item \textbf{Diffuse Lighting} - Setting this value higher will cause the surface to re-emit a higher proportion of light.
    \item \textbf{Specular Lighting} - The lighting which appears on the surface when illuminated.
    \item \textbf{Roughness Lighting} - The amount of light reflected by the roughness of the surface.
    \item \textbf{Fresnel Lighting} - Higher values create a wider, softer lighting across the surface.
\end{enumerate}
